Bayesian Modeling and Test Planning for Multi-phase Reliability Assessment

### 2017-12-15 paperDraft3.tex
getting close

\author{Kassandra M.\ Fronczyk\\Institute for Defense Analyses\\Alexandria, VA\\\texttt{kfronczy@ida.org} \and
Alyson G.\ Wilson\\North Carolina State University\\Raleigh, NC\\\texttt{agwilso2@ncsu.edu} \and
James F.\ Gilman\\North Carolina State University\\Raleigh, NC\\\texttt{jfgilman@ncsu.edu}
}
\maketitle} \fi

@@

The methodology section is organized as follows... section 3.1...

@@

% not sure we need this paragraph %
The Phase 1 analysis yields an estimate of the failure rate $\lambda_{ij}$ for
each of the vehicles for failure modes that are related.  We are assuming the
vehicles are conditionally independent, if we also assume the miles at failure
come from an exponential distribution the overall failure rate across all
failure modes can be easily calculated by $\sum_{j}\lambda_{j}$.  The
exponential distribution is commonly used in reliability analysis because of its
convenience, but as we will discuss in later sections it can be unrealistic in
many real-world situations.

\subsubsection{Fix Effectiveness}
After the first CAP, Test Phase 2 begins with the repaired vehicles. To capture
these revisions, the PM2 reliability growth model \cite{EH06} is often used.
This model explicitly captures testing phases, choices about which failure modes
to correct, and the potential of not completely eliminating a failure upon
repair. One of the downsides of PM2 is that many parameters of potential
interest, such as the Fix Effectiveness Factor (FEF), which measures how much
repairs improve failure rates, are typically fixed. A common value for FEF is
0.70. We follow the premise of this type of model, but allow a more flexible and
data-driven result that is less dependent on hard-coded assumptions.

@@

Despite its common uses the assumption of a constant hazard rate over time is
rarely justifiable.  It has been well documented the issues that can arise when
this assumption is violated ~\cite{ref2}.  Thus we will also consider the same
hierarchical model structure while using the Weibull distribution.  Now we
assume that the failure mileage $t_{ijk}$ each follow a $Weibull(\lambda, \gamma)$
distribution with scale parameter $\lambda$ and shape parameter $\gamma$, with
probability density function,
\begin{equation*}
    f(t_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
    t_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} t_{ijk}^{\gamma_{i}}).
\end{equation*}
The Weibull distribution is a more flexible model with both a rate parameter
$\lambda_{ij}$ and a shape parameter $\gamma_{j}$.  The exponential is a special
case of the Weibull, when $\gamma = 1$.  You should notice here we are now
modeling the actual failure mileage $t_{ijk}$ instead of the miles between
failures $y_{ijk}$.  This means we are treating all intra-test repairs as "bad
as old".  We could have continued with the miles between failures and assumed
"good as new" repairs, but "bad as old" modeling will be more convenient for
developing assurance test plans in later sections.  This distinction is
important in the Weibull case because the failure rate is not constant in time.
In practice the decision on intra-test repair assumptions should be made based
on the application.  In many cases repairs should be treated as somewhere
between "good as new" and "bad as old".  This requires more complex modeling
that is beyond the scope of this paper.

@@

\subsubsection{JLTV Reliability}
So far we have discussed a number of different models and the assumptions that
accompany them.  Using McMC we can fit each of these models to the JLTV dataset.
Then we can use the posterior distributions of the systems parameters to
estimate reliability-related quantities of interest for each of the eight
vehicle types.  We are able to look at a number of different statistics related
to reliability at both  the component and system level.  In this study our main
quantity of interest is expected miles to  failure.  In the following figure we
have box plots showing the posterior distributions of  the expected miles to
failure for one of the vehicle types for each of the three phases, first using
the exponential model and second using the more general Weibull model.

% going to add a table that will have the posterior means and 90% credible
% interval limits
\begin{figure}[h]
  \centering
      \includegraphics[width=9cm, height=7cm]{Boxplots}
  \caption{Comparing EMTF for Different Models}
\end{figure}

Figure 1 show that the posterior distributions from the Weibull model have a
good amount more spread than the exponential.  This is somewhat expected given
the Weibull model is estimating two model parameters to the exponentials one,
but what is concerning is that the center of the distributions is also quite
different between the two models.  All of the Weibull EMTF posterior means
are higher than the exponentials.  This is the first sign that the exponential
model may not be a good fit to the data.

@@

Here we have shown that the hierarchical Weibull model fits the data much better
than the exponential, but in general information criteria comparisons do not
tell us if the model is truly a good representation of the underlying process.
The last method we present is called posterior predictive checking ~\cite{ref3}.
Here we are given important features of the data that we would expect to see if
the experiment was repeted.  In the JLTV case one feature we were interested in
was the number of miles between failure observations that were less than 140
miles.  We then used the final models to simulate 5,000 new datasets for
vehicles tested over the same number of miles for each of the three phases. We
then plot the resulting distributions for each of the 8 vehicles for all 3
phases.  In Figure 3 are two examples of the boxplots produced, one from the
exponential model (left) and one from the Weibull model (right), with the dashed
line showing where the value from the observed dataset fell.  For this method we
don’t expect all of the true values to fall in the center of the distribution.
Some values in the tales are to be expected in a random processes like this one,
but when we see many observations in the tails, as we do with the exponential,
we should consider other modeling options.

\begin{figure}[h!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{PPExpo}
  %\caption{}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{PPWeibull}
  %\caption{}
  \label{fig:sub2}
\end{subfigure}
\caption{Posterior Predictive Plots \\ Exponential vs. Weibull}
\label{fig:test}
\end{figure}

\subsection{Assurance Test Planning}
In this section, we will use the reliability models fit in section two section
to develop a plan for future testing.  Here the objective is to demonstrate that
at a desired level of confidence, the system will meet or exceed a specified
requirement. The methods to be employed will be similar to the assurance testing
as discussed by Hamada et al. ~\cite{ref4}. Bayesian \emph{reliability assurance
tests} are used to ensure that the reliability of an item meets or exceeds a
specified requirement with a desired probability. Meeker and Escobar
~\cite{ME04} established the difference between this and the more traditional
\emph{reliability demonstration test}.  The difference being that the assurance
test plan incorporates supplementary data and information, where the
demonstration test only uses test data.

@@

\subsubsection{Classical Approach}
In the frequentest (classical) version we will use two criteria in determining
the test plans. The \emph{producer's risk}, defined as the probability of
failing the test when $\pi = \pi_0$, and the \emph{consumer's risk}, defined as
the probability of passing the test when $\pi = \pi_1$.  Suppose that we specify
a maximum value, $\alpha$, of the producer's risk and a maximum value, $\beta$,
of the consumer's risk. For test planning, these criteria become
$$
\begin{aligned}
	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\ &=
	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha
\end{aligned}
$$
and
$$
\begin{aligned}
	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\ &=
	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta
\end{aligned}
$$
To choose a test plan for specified values of $(\alpha, \pi_0, \beta, \pi_1)$,
we assume a distributional form that defines the relationship between the number
of system failures $W(t)$ and the reliability $\pi$.  Then we can simply find
the combinations of these probabilities by simultaneously solving these two
equations.  In the case where the component failure times are assumed to be
exponentially distributed with rate parameter $\lambda_i$ the failure counts for
each component come from a homogeneous Poisson process $w_i(t) \sim
\text{Poisson}(\lambda_i t)$, and the system failure counts $W(t) \sim
\text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
this purely classical approach.

@@

\begin{table}[h]
\center
\begin{tabular}{|l|l|r|}
\multicolumn{2}{c}{\textbf{JLTV Test Plan}} \\
\cline{1-2}
Failures Allowed    & Test Miles Required \\
\hline
0   & 5,500      \\
1   & 10,100      \\
2   & 17,900      \\
3   & 30,800     \\
4   & 51,200     \\
\hline
\end{tabular}
\end{table}

% This part should be expanded quite a bit and will extend into the discussion
% section.
It should be noted that if $\pi_0$, $\pi_1$, $\alpha$ and $\beta$ are set to
unrealisitc values there can be situations where no combinations of failures
allowed and test miles required will satisfy these probability statements.  In
this paper we have focused on test plans for single units, but this methodology
can be extended to find test plans that allow for a changing number of testing
units.  In this case you would find combinations of failures allowed and test
miles required and number of vehicles tested that satisfy the risk requirements.
More details and examples of this can be found in the assurance testing section
of Hamada et al. ~\cite{ref4}

\subsection{Discussion}

%%%%% ref %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of
system reliability availability maintainability - A primer; Third Edition
(1982).
\bibitem{ref2} National Research Council. Statistics, Testing, and Defense
Acquisition: Background Papers. \textit{National Academies Press} (1999).
\bibitem{ref3} Gelman, Andrew, Xiao-Li Meng, and Hal Stern. "Posterior
predictive assessment of model fitness via realized discrepancies."
\textit{Statistica sinica} 733-760 (1996).
\bibitem{ref4} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
Bayesian Reliability. Springer (2008).
\bibitem{ME04} W.\ Q.\ Meeker and L.\ A.\
Escobar. Reliability: the other dimension of quailty. \textit{Quality Technology
and Quantitative Management} 1, 1-25 (2004). \bibitem{HWWGM13} M.\ S.\ Hamada,
A.\ G.\ Wilson, B.\ P.\ Weaver, R.\ W.\ Griffiths and H.\ F.\ Martz. Bayesian
binomial assurance tests for system reliability using component data.
\textit{Journal of Quality Technology} 46, 24-32 (2014). \bibitem{JGHR03} V.\
E.\ Johnson, T.\ L.\ Graves, M.\ S.\ Hamada, and C.\ S.\ Reese. A hierarchical
model for estimating the reliability of complex systems. In Bayesian Statistics,
Vol. 7,\ J.\ M.\ Bernardo, M.\ J.\ Bayerri, J.\ O.\ Berger, A.\ P.\ Dawid, D.\
Heckerman, A.\ F.\ M.\ Smith, and M.\ West eds., Oxford, UK: Oxford University
Press (2003). \bibitem{HMRGJW04} M.\ S.\ Hamada, H.\ F.\ Martz, C.\ S.\ Reese,
T.\ L.\ Graves, V.\ E.\ Johnson, and A.\ G.\ Wilson. A fully Bayesian approach
for combining multilevel failure information in fault tree quantification and
optimal follow-on resource allocation. \textit{Reliability Engineering and
System Safety} 86, 397-405 (2004). \bibitem{EH06} P.\ M.\ Ellner and J.\ B.\
Hall, An approach to reliability growth planning based on failure mode discovery
and correction using AMSAA projection methodology. \textit{IEEE Proceedings of
the Annual Reliability and Maintainability Symposium} (2006).
\end{thebibliography}

@@

\begin{align*}
\lambda_i|\cdot &\sim \text{Gamma}(n_i + \alpha, \sum_{j=1}^{n_i}y_{ij}p^* + \beta) \\
\beta|\cdot &\sim \text{Gamma}(8\alpha + b_1, \sum{\lambda_i} + b_2) \\
\rho^{P2}|\cdot &\sim \text{Gamma}(N_{1,2} + c_1, \sum{y_{ij}\lambda_i} + c_2) \\
\rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{y_{ij}\lambda_i} + d_2) \\
\alpha|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}
\end{align*}

@@

\begin{align*}
\lambda_i|\cdot &\sim \text{Gamma}(n_i + \alpha, \sum_{j=1}^{n_i}t_{ij}^{\gamma_i} p^* + \beta) \\
\beta|\cdot &\sim \text{Gamma}(8\alpha + b_1, \sum{\lambda_i} + b_2) \\
\rho^{P2}|\cdot &\sim \text{Gamma}(N_{1,2} + c_1, \sum{t_{ij}^{\gamma_i} \lambda_i} + c_2) \\
\rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{t_{ij}^{\gamma_i} \lambda_i} + d_2) \\
\alpha|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}\\
\gamma|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}
\end{align*}

>>>>

\author{Kassandra M.\ Fronczyk\\Lawrence Livermore National Laboratory\\Livermore, CA\\\texttt{fronczyk1@llnl.gov} \and
Alyson G.\ Wilson\\North Carolina State University\\Raleigh, NC\\\texttt{agwilso2@ncsu.edu} \and
James F.\ Gilman\\North Carolina State University\\Raleigh, NC\\\texttt{jfgilman@ncsu.edu}
}
\maketitle} \fi

@@

The methodology section is organized as follows.  Section 3.1 describes the
reliability modeling process, breaking it down into five subsections.  First, we
introduce the general structure we will be using along and how to account for
the correction period between phases.  Then we move onto distributional
assumptions and model diagnostics which we illistrate with the JLTV case study
data.  In section 3.2 we discuss methods of designing next stage test plans.
First we outline the traditional approaches, then we walk through a Bayesian
approach that allows the practitioner to incorperating the models developed from
section 3.1 with the hopes of reducing testing resources required while still
minimizing producer and consumer risks.

@@

% not sure we need this paragraph %
The Phase 1 analysis yields an estimate of the failure rate $\lambda_{ij}$ for
each of the vehicles for failure modes that are related.  We are assuming the
vehicles are conditionally independent, if we also assume the miles at failure
come from an exponential distribution the overall failure rate across all
failure modes can be easily calculated by $\sum_{j}\lambda_{j}$ to give us the
system failure rate.  The exponential distribution is commonly used in
reliability analysis because of its convenience, but as we will discuss in later
sections it can be unrealistic in many real-world situations.

\subsubsection{Fix Effectiveness}
After the first CAP, Test Phase 2 begins with the repaired vehicles. To capture
these revisions, the PM2 reliability growth model \cite{ref2} is often used.
This model explicitly captures testing phases, choices about which failure modes
to correct, and the potential of not completely eliminating a failure upon
repair. One of the downsides of PM2 is that many parameters of potential
interest, such as the Fix Effectiveness Factor (FEF), which measures how much
repairs improve failure rates, are typically fixed. A common value for FEF is
0.70. We follow the premise of this type of model, but allow a more flexible and
data-driven result that is less dependent on hard-coded assumptions.

@@

Despite its common uses the assumption of a constant hazard rate over time is
rarely justifiable.  It has been well documented the issues that can arise when
this assumption is violated ~\cite{ref3}.  Thus we will also consider the same
hierarchical model structure while using the Weibull distribution.  Now we
assume that the failure mileage $t_{ijk}$ each follow a $Weibull(\lambda, \gamma)$
distribution with scale parameter $\lambda$ and shape parameter $\gamma$, with
probability density function,
\begin{equation*}
    f(t_{ijk}|\lambda_{ij},\gamma_{i})=\lambda_{ij}\gamma_{i}
    t_{ijk}^{\gamma_{i}-1}\exp(-\lambda_{ij} t_{ijk}^{\gamma_{i}}).
\end{equation*}
The Weibull distribution is a more flexible model with both a rate parameter
$\lambda_{ij}$ and a shape parameter $\gamma_{j}$.  The exponential is a special
case of the Weibull, when $\gamma = 1$.  You should notice here we are now
modeling the actual failure mileage $t_{ijk}$ instead of the miles between
failures $y_{ijk}$.  This means we are treating all intra-test repairs as "bad
as old".  We could have continued with the miles between failures and assumed
"good as new" repairs, but "bad as old" modeling will be more convenient for
developing assurance test plans in later sections.  This distinction is
important in the Weibull case because the failure rate is not constant in time.
In practice the decision on intra-test repair assumptions should be made based
on the application.  In many cases repairs should be treated as somewhere
between "good as new" and "bad as old".  This requires more complex modeling
that is beyond the scope of this paper.

@@

\subsubsection{JLTV Reliability}
So far we have discussed a number of different models and the assumptions that
accompany them.  Using McMC we can fit each of these models to the JLTV dataset.
Then we can use the posterior distributions of the systems parameters to
estimate reliability-related quantities of interest for each of the eight
vehicle types.  We are able to look at a number of different statistics related
to reliability at both the component and system level.  In this study our main
quantity of interest is expected miles to  failure.  In figure 1 we have box
plots and summary statistics from the posterior distributions of the expected
miles to failure for one of the vehicle types for each of the three phases,
first using the exponential model and second using the more general Weibull
model.

\begin{figure}[h!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
      \includegraphics[width=9cm, height=7cm]{Boxplots}
  % \caption{Comparing EMTF for Different Models}
  %\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \center
  \begin{tabular}{|c|c|c|c|c|}
  \multicolumn{5}{c}{\textbf{Summary Statistics}} \\
  \cline{1-5}
  Model & Phase & Mean & 90\% CI Low & 90\% CI Up \\
  \hline
  Expo & P1   & 129.98   & 110.22 &  152.23 \\
  Expo & P2   & 98.44  & 89.00 &  108.38  \\
  Expo & P3   & 135.89   & 117.78 &  155.45 \\
  Weibull & P1   & 169.96  & 116.95 & 236.16 \\
  Weibull & P2   & 135.24   & 104.89 & 167.48 \\
  Weibull & P3   & 175.51   & 138.87 & 214.23 \\
  \hline
  \end{tabular}
  %\label{fig:sub2}
\end{subfigure}
\caption{Comparing EMTF for Different Models}
\label{fig:test}
\end{figure}

You can see the posterior distributions from the Weibull model have a good
amount more spread than the exponential.  This is somewhat expected given the
Weibull model is estimating two model parameters to the exponentials one, but
what is concerning is that the center of the distributions is also quite
different between the two models.  All of the Weibull EMTF posterior means are
higher than the exponentials.  This is the first sign that the exponential model
may not be a good fit to the data.

@@

Here we have shown that the hierarchical Weibull model fits the data much better
than the exponential, but in general information criteria comparisons do not
tell us if the model is truly a good representation of the underlying process.
The last method we present is called posterior predictive checking ~\cite{ref4}.
Here we are given important features of the data that we would expect to see if
the experiment was repeted.  In the JLTV case one feature we were interested in
was the number of miles between failure observations that were less than 140
miles.  We then used the final models to simulate 5,000 new datasets for
vehicles tested over the same number of miles for each of the three phases. We
then plot the resulting distributions for each of the 8 vehicles for all 3
phases.  In Figure 3 are two examples of the boxplots produced, one from the
exponential model (left) and one from the Weibull model (right), with the dashed
line showing where the value from the observed dataset fell.  For this method we
don’t expect all of the true values to fall in the center of the distribution.
Some values in the tales are to be expected in a random processes like this one,
but when we see many observations in the tails, as we do with the exponential,
we should consider other modeling options.

\begin{figure}[h!]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{PPExpo}
  %\caption{}
  %\label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{PPWeibull}
  %\caption{}
  %\label{fig:sub2}
\end{subfigure}
\caption{Posterior Predictive Plots \\ Exponential vs. Weibull}
%\label{fig:test}
\end{figure}

\subsection{Assurance Test Planning}
In this section, we will use the reliability models fit in section two section
to develop a plan for future testing.  Here the objective is to demonstrate that
at a desired level of confidence, the system will meet or exceed a specified
requirement. The methods to be employed will be similar to the assurance testing
as discussed by Hamada et al. ~\cite{ref5}. Bayesian \emph{reliability assurance
tests} are used to ensure that the reliability of an item meets or exceeds a
specified requirement with a desired probability. Meeker and Escobar
~\cite{ref6} established the difference between this and the more traditional
\emph{reliability demonstration test}.  The difference being that the assurance
test plan incorporates supplementary data and information, where the
demonstration test only uses test data.

@@

\subsubsection{Classical Approach}
In the frequentest (classical) version we will use two criteria in determining
the test plans. The \emph{producer's risk}, defined as the probability of
failing the test under the null hypothesis $\pi = \pi_0$, and the
\emph{consumer's risk}, defined as the probability of passing the test under an
alternative hypothesis $\pi = \pi_1$.  Suppose that we specify a maximum value,
$\alpha$, of the producer's risk and a maximum value, $\beta$, of the consumer's
risk. For test planning, these criteria become
$$
\begin{aligned}
	\text{Producer's Risk} &= P \text{(Test Is Failed } \vert \pi_0 \text{)} \\ &=
	P \text{(} W(t) > c \vert \pi_0 \text{)} \leq \alpha
\end{aligned}
$$
and
$$
\begin{aligned}
	\text{Consumer's Risk} &= P \text{(Test Is Passed } \vert \pi_1 \text{)} \\ &=
	P \text{(} W(t) \leq c \vert \pi_1 \text{)} \leq \beta
\end{aligned}
$$
To choose a test plan for specified values of $(\alpha, \pi_0, \beta, \pi_1)$,
we assume a distributional form that defines the relationship between the number
of system failures $W(t)$ and the reliability $\pi$.  Then we can simply find
the combinations of these probabilities by simultaneously solving these two
equations.  In the case where the component failure times are assumed to be
exponentially distributed with rate parameter $\lambda_i$ the failure counts for
each component come from a homogeneous Poisson process $w_i(t) \sim
\text{Poisson}(\lambda_i t)$, and the system failure counts $W(t) \sim
\text{Poisson}(\lambda_S t)$.  Numerous textbooks provide additional details of
this purely classical approach.

@@

\begin{table}[h]
\center
\begin{tabular}{|c|c|}
\multicolumn{2}{c}{\textbf{JLTV Test Plan}} \\
\cline{1-2}
Failures Allowed    & Test Miles Required \\
\hline
0   & 5,500     \\
1   & 10,100    \\
2   & 17,900    \\
3   & 30,800    \\
4   & 51,200    \\
\hline
\end{tabular}
\end{table}

These results alone do not provide much insite into how well the method is
performing. A natural comparison would be with the frequentest test plan in this
setting.  In general  we warn against this comparison because the test plan
probability constrants for each  method are asking different questions.  The
frequentest plan controls the error rates  under two different assumed settings.
On the other hand, the Bayesian plan puts constrants  on the error when the test
is passed and failed.  We would argue that in most settings  the Bayesian plan
controls for the error the practitioner cares about.  In this case there are no
reasonable combinations of allowed failures and required test miles  that
satisfy both producer's and consumer's risk probability statements in the
frequentest test plan.
Both test planning approaches rely heavily on setting reasonable values for
$\pi_0$, $\pi_1$, $\alpha$ and $\beta$.   When these are set to unrealisitc
values both proceedures can can result in no plan that satisfies the probability
statements.  In this paper we have focused on test plans for single units, but
th the assurance testing methodology can be extended to find test plans that
allow for a changing number of testing units.  In this case you would find
combinations of failures allowed and test miles required and number of vehicles
tested that satisfy the risk requirements. More details and examples of this can
be found in the assurance testing section of Hamada et al. ~\cite{ref5}

\subsection{Discussion}
The JLTV case study results provide indications that our model is successfully
capturing the failure rates across failure modes, inferring logical fix
effectiveness factor distributions, and providing reliability estimates that can
be leveraged for future test planning. In the traditional analysis, we do not
typically look at failure rates of the failure modes, nor would we be able to
leverage the commonalities across vehicles. The proposed modeling framework
overcomes these limitations and allows for more realistic reliability estimates
for vehicles with no observed failures. Additionally, our data-driven approach
for reliability growth improves on the current growth models being used in the
DoD, which are based solely on fixed quantities set by management.

While our basic approach provides reasonable initial inferences, there are
several extensions to incorporate. For example, reliability estimates for
vehicles with no observed failures are sensible; however, we should leverage
more information across vehicles. Because the correlations induced by our
current model are fairly low, potential methods for inducing more correlation
between the vehicles in the related failure modes are being investigated. We
also need to look more closely at the intra-phase repair assumptions.  Appling
repairable system  methodology in the modeling and reliability assesment stage
could be a good approach, but this could  add a great deal of complexity to the
assurance planning stage.

%%%%% ref %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}
\bibitem{ref1} Director, Defense Test and Evaluation. Test and evaluation of system reliability availability maintainability - A primer; Third Edition (1982).
\bibitem{ref2} P.\ M.\ Ellner and J.\ B.\ Hall, An approach to reliability
growth planning based on failure mode discovery and correction using AMSAA
projection methodology. \textit{IEEE Proceedings of the Annual Reliability and
Maintainability Symposium} (2006).
\bibitem{ref3} National Research Council. Statistics, Testing, and Defense
Acquisition: Background Papers. \textit{National Academies Press} (1999).
\bibitem{ref4} Gelman, Andrew, Xiao-Li Meng, and Hal Stern. "Posterior
predictive assessment of model fitness via realized discrepancies."
\textit{Statistica sinica} 733-760 (1996).
\bibitem{ref5} M.\ S.\ Hamada, A.\ G.\ Wilson, C.\ S.\ Reese and H.\ F.\ Martz.
Bayesian Reliability. Springer (2008).
\bibitem{ref6} W.\ Q.\ Meeker and L.\ A.\ Escobar. Reliability: the other
dimension of quailty. \textit{Quality Technology and Quantitative Management} 1,
1-25 (2004).
\end{thebibliography}

@@

Full conditionals for Gibbs sampling:
\begin{align*}
\lambda_i|\cdot &\sim \text{Gamma}(n_i + \alpha, \sum_{j=1}^{n_i}y_{ij}p^* + \beta) \\
\beta|\cdot &\sim \text{Gamma}(8\alpha + b_1, \sum{\lambda_i} + b_2) \\
\rho^{P2}|\cdot &\sim \text{Gamma}(N_{1,2} + c_1, \sum{y_{ij}\lambda_i} + c_2) \\
\rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{y_{ij}\lambda_i} + d_2) \\
\alpha|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}
\end{align*}

@@

Full conditionals for Gibbs sampling:
\begin{align*}
\lambda_i|\cdot &\sim \text{Gamma}(n_i + \alpha, \sum_{j=1}^{n_i}t_{ij}^{\gamma_i} p^* + \beta) \\
\beta|\cdot &\sim \text{Gamma}(8\alpha + b_1, \sum{\lambda_i} + b_2) \\
\rho^{P2}|\cdot &\sim \text{Gamma}(N_{1,2} + c_1, \sum{t_{ij}^{\gamma_i} \lambda_i} + c_2) \\
\rho^{P3}|\cdot &\sim \text{Gamma}(N_{2} + d_1, \sum{t_{ij}^{\gamma_i} \lambda_i} + d_2) \\
\alpha|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}\\
\gamma|\cdot &\sim \text{Unknown form.  Used Metropolis-Hastings.}
\end{align*}
